Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-09-08 manuscript.Rmd
Added github repo

EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox [@Delorme2004]. The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds). The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix. All repetitions of each condition were then averaged for each electrode. They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results. Finally, these were averaged across participants to obtain the group results. All averaging was performed in the complex domain and therefore retained the phase information (i.e. coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean [see @Baker2021]. For statistical comparisons of complex-valued data, we use the $ANOVA^2_{circ}$ statistic described by @Baker2021. This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the $T^2_{circ}$ statistic of @Victor1991 that can compare more than two conditions.

>>>>

EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script (available at: https://github.com/bakerdh/PupillometryEEG/; @Segala2023) and components of the EEGlab toolbox [@Delorme2004]. The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds). The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix. All repetitions of each condition were then averaged for each electrode. They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results. Finally, these were averaged across participants to obtain the group results. All averaging was performed in the complex domain and therefore retained the phase information (i.e. coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean [see @Baker2021]. For statistical comparisons of complex-valued data, we use the $ANOVA^2_{circ}$ statistic described by @Baker2021. This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the $T^2_{circ}$ statistic of @Victor1991 that can compare more than two conditions.

### 2023-09-08 manuscript.tex
Added github repo

EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (Delorme and Makeig, \protect\hyperlink{ref-Delorme2004}{2004}). The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds). The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix. All repetitions of each condition were then averaged for each electrode. They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results. Finally, these were averaged across participants to obtain the group results. All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (see Baker, \protect\hyperlink{ref-Baker2021}{2021}). For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by Baker (\protect\hyperlink{ref-Baker2021}{2021}). This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of Victor and Mast (\protect\hyperlink{ref-Victor1991}{1991}) that can compare more than two conditions.

@@

>>>>

EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script (available at: \url{https://github.com/bakerdh/PupillometryEEG/}; Segala et al. (\protect\hyperlink{ref-Segala2023}{2023})) and components of the EEGlab toolbox (Delorme and Makeig, \protect\hyperlink{ref-Delorme2004}{2004}). The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds). The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix. All repetitions of each condition were then averaged for each electrode. They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results. Finally, these were averaged across participants to obtain the group results. All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (see Baker, \protect\hyperlink{ref-Baker2021}{2021}). For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by Baker (\protect\hyperlink{ref-Baker2021}{2021}). This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of Victor and Mast (\protect\hyperlink{ref-Victor1991}{1991}) that can compare more than two conditions.

@@

\leavevmode\hypertarget{ref-Segala2023}{}%
Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH. 2023. Different rules for binocular combination of luminance flicker in cortical and subcortical pathways (code). Github. Https://github.com/bakerdh/pupillometryeeg/. F3181b1.
